---
title: "Alpha Test 02 - If A and B and C for Random Weekday"
author: "David Ory"
runtime: shiny
output:
  html_document:
    theme: cosmo
    toc: yes
---

## Administration

#### Purpose
Examine a month of the anonymized Clipper data to try and find rare, but persistent, patterns, that may allow a third-party consumer of the data to identify individual travelers.  This is part of the pre-release anonymized Clipper data alpha testing.  In this test, sequences by day are presented for sequences that contain specific segments. Note that this version of the anonmyzed data suppresses the actual date, instead providing a year, month, day of week, and week indicator.

#### Note
1 A bit too heavy for MacBook

## Procedure

#### Overhead
```{r overhead}
library(knitr)
suppressMessages(library(dplyr))
library(shiny)
library(ggplot2)
#setwd("M:/Data/Clipper/Alpha Tests/_working")
setwd("~DavidWork/Documents/Clipper")
```

```{r config, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

#### Read in the sequence data
```{r data_reads}
#input.seq = read.table(file = "M:/Data/Clipper/Alpha Tests/_working/Sequence Frequencies for Random Weekday.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
input.seq = read.table(file = "~DavidWork/Documents/Clipper/Sequence Frequencies for Random Weekday.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
```

#### Prepare all sequence data
```{r prep_all}
all.seq <- input.seq %.%
  group_by(CircadianDayOfWeek, RandomWeekID) %.%
  summarise(Cards = sum(n))
head(all.seq, n = 30)
```

#### Plot all data
```{r shiny_plot_all, echo=FALSE, cache=FALSE}
renderPlot({
  
  all.seq$weekday_order <- factor(all.seq$CircadianDayOfWeek, c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))
  
  plot <- ggplot(all.seq, aes(x = weekday_order, y = Cards)) + geom_point(size = 4, colour = "#0072B2") + xlab("Day of Week March 2013") + ylab("Clipper Cards Used") + ggtitle("All Clipper Cards") + theme(text = element_text(size=15), axis.text.x = element_text(vjust=1), axis.title.y = element_text(vjust=2.0), legend.position="none")
  
  print(plot)
}, height = 600)

```

## Interactives

### Three-Filter Plot
```{r shiny_plot_threefilter, echo=FALSE, cache=FALSE}

textInput("Filter01", "Sequences that contain:", "S")
textInput("Filter02", "And also contain:", "F")
textInput("Filter03", "And also contain:", "M")

renderPlot({
  
  chart.data <- input.seq %.%
    filter(grepl(input$Filter01, RunSequence)) %.%
    mutate(WorkingSequence = RunSequence) %.%
    mutate(WorkingSequence = gsub(input$Filter01,"", WorkingSequence)) %.%
    filter(grepl(input$Filter02, WorkingSequence)) %.%
    mutate(WorkingSequence = gsub(input$Filter02, "", WorkingSequence)) %.%
    filter(grepl(input$Filter03, WorkingSequence)) %.%
    group_by(CircadianDayOfWeek, RandomWeekID) %.%
    summarise(Cards = sum(n))
  
  chart_title <- paste("Sequences with ", "'", input$Filter01, "'", " and ", "'", input$Filter02, "'", " and ", "'", input$Filter03, "'")
  
  chart.data$weekday_order <- factor(chart.data$CircadianDayOfWeek, c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday"))

  plot <- ggplot(chart.data, aes(x = weekday_order, y = Cards)) + geom_point(size = 4, colour = "#D55E00") + xlab("Day of Week March 2013") + ylab("Clipper Cards Used") + labs(title = chart_title) + theme(text = element_text(size=15), axis.text.x = element_text(vjust=1), axis.title.y = element_text(vjust=2.0), legend.position="none")
  
  print(plot)
  
  }, height = 600)

```

### Three-Filter Table
```{r shiny_table_threefilter, echo=FALSE, cache=FALSE}

renderTable({
  
  table.data <- input.seq %.%
    filter(grepl(input$Filter01, RunSequence)) %.%
    mutate(WorkingSequence = RunSequence) %.%
    mutate(WorkingSequence = gsub(input$Filter01,"", WorkingSequence)) %.%
    filter(grepl(input$Filter02, WorkingSequence)) %.%
    mutate(WorkingSequence = gsub(input$Filter02, "", WorkingSequence)) %.%
    filter(grepl(input$Filter03, WorkingSequence)) %.%
    select(Year, Month, CircadianDayOfWeek, RandomWeekID, RunSequence, Count = n)
  
  head(table.data, n = 100)
   
  })

```

