---
title: "Alpha Test 01 - Examine Sequences"
author: "David Ory"
runtime: shiny
output:
  html_document:
    toc: true
    theme: cosmo
---

## Administration

#### Purpose
Examine a month of the anonymized Clipper data to try and find rare, but persistent, patterns, that may allow a third-party consumer of the data to identify individual travelers.  This is part of the pre-release anonymized Clipper data alpha testing.

#### Outputs
1 Simple Shiny tables of rare and common sequences.

## Procedure

#### Overhead
```{r overhead}
library(knitr)
suppressMessages(library(dplyr))
suppressMessages(library(plyr))
library(shiny)
# setwd("M:/Data/Clipper/Alpha Tests/_working")
setwd("~DavidWork/Documents/Clipper")
```

```{r config, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

#### Read in the sequence data
```{r data_reads}
#input.seq = read.table(file = "./Sequence Frequencies by Date.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
input.seq = read.table(file = "~DavidWork/Documents/Clipper/Sequence Frequencies by Date.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(input.seq, n = 10)
```

#### Explore typical weekdays
```{r typical_weekdays}
seq.typical <- mutate(input.seq, CircadianDayOfWeek = weekdays(as.Date(input.seq$CircadianDate)))
seq.typical <- filter(seq.typical, CircadianDayOfWeek == "Tuesday" | CircadianDayOfWeek == "Wednesday" |CircadianDayOfWeek == "Thursday")
seq.typical <- select(seq.typical, CircadianDate, RunSequence, Count = n)
seq.sum <- ddply (seq.typical, .(RunSequence), summarise, SumFreq = sum(Count), MedianFreq = median(Count), MinFreq = min(Count), MaxFreq = max(Count))

```

#### Sequences that occur EVERY typical weekday
```{r every_typical}
every.typical <- tally(group_by(seq.typical, RunSequence), wt = NULL, sort = TRUE)
every.typical <- filter(every.typical, n == length(unique(seq.typical$CircadianDate)))
every.typical <- select(every.typical, -n)
every.seq <- left_join(x = every.typical, y = seq.sum, by = "RunSequence")
every.seq <- select(every.seq, -SumFreq)
every.seq <- arrange(every.seq, desc(MedianFreq))
```

#### Sequences that occur ONLY ONCE EVERY typical weekday
```{r rare_typical}
rare.typical <- filter(every.seq, (MinFreq == 1) & (MaxFreq == 1))
rare.typical <- select(rare.typical, RunSequence, MinFreq, MaxFreq)
```

#### Sequences that occur MOST COMMONLY EVERY typical weekday
```{r common_typical}
common.typical <- filter(every.seq, percent_rank(MedianFreq) > 0.95)
common.typical <- arrange(common.typical, desc(MedianFreq))
```

## Interactives

#### Sequences that occur ONLY ONCE EVERY typical weekday (Total = `r nrow(rare.typical) `)
```{r rare_typical_shiny, echo=FALSE, cache=FALSE}
numericInput("rows", "How many rows would you like to see?", 50)
renderTable({head(rare.typical, input$rows)})
```

#### Sequences that occur EVERY typical weekday that contain ...
```{r common_typical_string_shiny, echo=FALSE, cache=FALSE}
textInput("Contains", "Route sequence contains:", "TYPE HERE")
renderTable({head(filter(every.seq, grepl(input$Contains,every.seq$RunSequence)), 50)})
```

