---
title: "Alpha Test 02 - If A and B and C"
author: "David Ory"
runtime: shiny
output:
  html_document:
    theme: cosmo
    toc: yes
---

## Administration

#### Purpose
Examine a month of the anonymized Clipper data to try and find rare, but persistent, patterns, that may allow a third-party consumer of the data to identify individual travelers.  This is part of the pre-release anonymized Clipper data alpha testing.  In this test, sequences by day are presented for sequences that contain specific segments.

#### TODO
1 Check memory on PC -- too heavy for Mac?

## Procedure

#### Overhead
```{r overhead}
library(knitr)
suppressMessages(library(dplyr))
library(shiny)
library(ggplot2)
#setwd("M:/Data/Clipper/Alpha Tests/_working")
setwd("~DavidWork/Documents/Clipper")
```

```{r config, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

#### Read in the sequence data
```{r data_reads}
#input.seq = read.table(file = "M:/Data/Clipper/Alpha Tests/_working/Sequence Frequencies by Date.csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
#input.seq = read.table(file = "M:/Data/Clipper/Alpha Tests/_working/Sequence Frequencies by Date (test).csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
input.seq = read.table(file = "~DavidWork/Documents/Clipper/Sequence Frequencies by Date (test).csv", header = TRUE, sep = ",", stringsAsFactors = FALSE)
```

#### Prepare all sequence data
```{r prep_all}
all.seq <- input.seq %.%
  mutate(DayOfMonth = substr(CircadianDate,9,10)) %.%
  group_by(DayOfMonth) %.%
  summarise(Cards = sum(n))
head(all.seq, n = 31)
```

#### Plot all data
```{r shiny_plot_all, echo=FALSE, cache=FALSE}
renderPlot({
  
  plot <- ggplot(all.seq, aes(x = DayOfMonth, y = Cards)) + geom_point(size = 4, colour = "#0072B2") + xlab("Day of April 2013") + ylab("Clipper Cards Used") + ggtitle("All Clipper Cards") + theme(text = element_text(size=15), axis.text.x = element_text(vjust=1), axis.title.y = element_text(vjust=2.0), legend.position="none")
  
  print(plot)
}, height = 600)

```

## Interactives

### Three-Filter Plot
```{r shiny_plot_threefilter, echo=FALSE, cache=FALSE}

textInput("Filter01", "Sequences that contain:", " ")
textInput("Filter02", "And also contain:", " ")
textInput("Filter03", "And also contain:", " ")

renderPlot({
  
  chart.data <- input.seq %.%
    filter(grepl(input$Filter01, RunSequence)) %.%
    mutate(WorkingSequence = RunSequence) %.%
    mutate(WorkingSequence = gsub(input$Filter01,"", WorkingSequence)) %.%
    filter(grepl(input$Filter02, WorkingSequence)) %.%
    mutate(WorkingSequence = gsub(input$Filter02, "", WorkingSequence)) %.%
    filter(grepl(input$Filter03, WorkingSequence)) %.%
    mutate(DayOfMonth = substr(CircadianDate,9,10)) %.%
    group_by(DayOfMonth) %.%
    summarise(Cards = sum(n))
  
  chart_title <- paste("Sequences with ", "'", input$Filter01, "'", " and ", "'", input$Filter02, "'", " and ", "'", input$Filter03, "'")

  plot <- ggplot(chart.data, aes(x = DayOfMonth, y = Cards)) + geom_point(size = 4, colour = "#D55E00") + xlab("Day of April 2013") + ylab("Clipper Cards Used") + labs(title = chart_title) + theme(text = element_text(size=15), axis.text.x = element_text(vjust=1), axis.title.y = element_text(vjust=2.0), legend.position="none")
  
  print(plot)
  
  }, height = 600)

```

### Three-Filter Table
```{r shiny_table_threefilter, echo=FALSE, cache=FALSE}

textInput("Filter01", "Sequences that contain:", " ")
textInput("Filter02", "And also contain:", " ")
textInput("Filter03", "And also contain:", " ")

renderTable({
  
  table.data <- input.seq %.%
    filter(grepl(input$Filter01, RunSequence)) %.%
    mutate(WorkingSequence = RunSequence) %.%
    mutate(WorkingSequence = gsub(input$Filter01,"", WorkingSequence)) %.%
    filter(grepl(input$Filter02, WorkingSequence)) %.%
    mutate(WorkingSequence = gsub(input$Filter02, "", WorkingSequence)) %.%
    filter(grepl(input$Filter03, WorkingSequence)) %.%
    select(CircadianDate, RunSequence, Count = n)
  
  head(table.data, n = 100)
   
  })

```

