---
title: "Build Transfer Database"
author: "David Ory"
output:
  html_document:
    theme: cosmo
    toc: yes
---
## Administration

Download the input data. This is for convenience. You can also get it from `M:/Data/Clipper` and set the appropriate data_dir below. 

```{r, eval=FALSE}
data_dir <- "/Users/tommtc/Data"
library(boxr)
box_auth()
box_fetch(dir_id=51200568211, local_dir = data_dir)
```

If you didn't download the data, set the data_dir here:

```{r, eval=FALSE}
data_dir <- "M:/Data/Clipper/Transfers/From Anonymous/extracts/"
```

#### Purpose

The anonymous Clipper data is potentially an excellent source for quantifying operator-to-operator transit movements.  Here, we seek to understand transfers in the travel model sense, i.e. a movement between an origin and destination that requires a tranfer between or within transit operators.  This definition differs from transfers as defined by certain transit agencies, which generally allow multiple boardings at no or reduced cost during a narrow time window.  Here, we implement a set of rules to build a database of transfers.  This script uses data derived from the anonymous Clipper data -- see `Extract Transfer for Random Weekday to CSV.R`.  Please see `To and From Interactive.Rmd` for an interactive charting engine of operator pairs.

```{r overhead}
library(knitr)
library(stringr)
library(ggplot2)
library(clpr)
suppressMessages(library(dplyr))
```

```{r config, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

```{r}
transfer_filenames_df <- arrange(transfer_filenames_df,year,month) 
```

```{r}
SAMPLING_RATE = 0.50

output_file_string <- "Transfers by day by agency pair.csv"

r1 <- apply(transfer_filenames_df[1,], 1, function(x) try(Build_Database(x, 
                                                              data_dir, 
                                                              transfer_rules_df, 
                                                              SAMPLING_RATE, 
                                                              output_file_string, 
                                                              FALSE)))
```
