---
title: "Extraction Examples"
author: "Tom Buckley"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This is a draft vignette of scripts originally written by David Ory. Please see the Git history for more detail. 

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Extract Sequence by Date to CSV.R

Take a month of data from the anonymized Clipper SQL server table, build transaction sequences for
each card holder, and push the data to a CSV for analysis in other Alpha test scripts.

note:2014 08 08 dto

```{r, fig.show='hold'}
suppressMessages(library(dplyr))
suppressMessages(library(plyr))
library(odbc)
library(stringr)
setwd("M:/Data/Clipper/Alpha Tests/_working")

rs <- dbConnect(odbc::odbc(), "Redshift")
sequence.freq <- extract_sequence_by_date(rs)

# Write sequence frequency to disk
write.csv(sequence.freq, file = "Sequence Frequencies by Date.csv", row.names = FALSE, quote = T)

```

## Extract Data by Month and Year

Take some amount of data from the anonymized Clipper SQL server table and push to CSV.

note: 2014 12 05 dto

```{r}

# Overhead
library(odbc)

# Get command line arguments
args <- commandArgs(trailingOnly = TRUE)

# Extract data a month at a time
MONTH_SELECT  = args[1]
YEAR_SELECT   = args[2]

library(DBI)
library(dbplyr)
library(dplyr)
library(readr)

#connect to dbs
rs <- dbConnect(odbc::odbc(), "Redshift")

extract_by_month_and_year_query <- read_file("inst/sql/extract_by_month_and_year.sql")
QUERY_STATEMENT = paste(extract_by_month_and_year_query,MONTH_SELECT,") AND (Year = ",YEAR_SELECT,")")
df_raw <- sqlQuery(rs, QUERY_STATEMENT)

# Write sequence frequency to disk
write.csv(df_raw, file = paste(YEAR_SELECT,"-",MONTH_SELECT," Anonymous Clipper Socrata.csv"), row.names = FALSE, quote = T)

odbcCloseAll()
```

## Extract Sequence for Random Weekday to CSV.R

Take a month of data from the anonymized Clipper SQL server table, build transaction sequences for
each card holder, and push the data to a CSV for analysis in other Alpha test scripts.  Note that
this version of the anonmyzed data suppresses the actual date, instead providing a year, month,
day of week, and week indicator.

note: 2014 08 08 dto

```{r}
suppressMessages(library(dplyr))
suppressMessages(library(plyr))
library(RODBC)
library(stringr)
setwd("M:/Data/Clipper/Alpha Tests/_working")

rs <- dbConnect(odbc::odbc(), "Redshift")

sequence.freq.join <- extract_sequence_for_random_week(rs)

# Write sequence frequency to disk
write.csv(sequence.freq.join, file = "Sequence Frequencies for Random Weekday.csv", row.names = FALSE, quote = T)
```
